Assignment 5

### 2015-02-25 rmtw/a5/latex8.tex
SADADSDS

The benefits of MDSD have consistently been reported in academia \cite{staron2006adopting} \cite{volter2013model}. Many large companies such as Ericsson and ABB \cite{staron2006adopting} also use MDSD as a part of their development chain. In industry, however, MDSD struggles to make a (full) (x-wide) (XXX) breakthrough and it is mostly used for niche systems such as embedded and safety-critical systems.

@@

\begin{itemize}
\item They are probably not worded optimally... Here're some alturnutuves:
\item In which situations should companies expect MDD to be successfully adopted?
\item In which situations should companies expect that the adoption of MDD would lead to a performance boost?
\end{itemize}

@@

It is important to note that did not perform either a Systematic Mapping Study nor a Tertiary Review of existing literature. There was sufficient evidence in existence for the applicability of MDSD such that we could rule out the need to perform a Systematic Mapping Study. Furthermore, there was insufficient SLRs that had been conducted prior to our study, thus, a Tertiary Review was not possible nor appropriate at that time.

\begin{itemize}
\item Describe and explain the research strategy (i.e. SLR) and investigation methods that will be used for the study. 
\item Motivate your choice of experiment using relevant references. 
\item Search string including keywords and used databases
\item inclusion/exclusion criteria
\item data extraction
\item data synthesis
\item quality assessment
\end{itemize}

kithcneham start

\textbf{Planning the review}
Initially, existing SLRs were identified and evaluated, with the goal of mapping and identifying the gap in the existing literature. All identified SLRs \cite{santiago2012model} \cite{dias2007survey} \cite{loniewski2010systematic} \cite{nicolas2009generation} were, however, researching the usage of model-driven techniques in other fields, such as traceability management \cite{santiago2012model}, testing \cite{dias2007survey} and requirements engineering \cite{loniewski2010systematic} \cite{nicolas2009generation}. Based on these results, the need to evaluate previous research on model driven \textit{software} development was identified.

The next step was to define the research questions. The main research question was constructed to create a wide scope to be able to investigate which characteristics are most vital to consider when adopting MDSD. The sub-questions were constructed to provide more detailed answers for specific questions that are valuable to the industry and companies who are condering to implement MDSD.

@@

\textbf{Conducting the review}
\begin{itemize}
\item Identification of research (6.1)

@@

\textbf{Reporting the review}
\begin{itemize}
\item Specifying dissemination mechanisms (7.1)
\item Formatting the main report (7.2)
\item Evaluating the report (7.3)
\end{itemize}

@@

\Section{Acknowledgements}
U w0T m8

>>>>

The benefits of MDSD have consistently been reported in academia \cite{staron2006adopting} \cite{volter2013model}. Many large companies such as Ericsson and ABB \cite{staron2006adopting} also use MDSD as a part of their development chain. In industry, however, MDSD has struggled to make a complete breakthrough and it is mostly used for niche systems such as embedded and safety-critical systems.

@@

\begin{itemize}
\item They are probably not worded optimally... Here're some alternatives:
\item In which situations should companies expect MDD to be successfully adopted?
\item In which situations should companies expect that the adoption of MDD would lead to a performance boost?
\end{itemize}

@@

It is important to note that did not perform either a Systematic Mapping Study nor a Tertiary Review of existing literature. There was sufficient evidence in existence for the applicability of MDSD such that we could rule out the need to perform a Systematic Mapping Study. Furthermore, there were insufficient SLRs that had been conducted prior to our study, thus, a Tertiary Review was not possible nor appropriate at that time.

\SubSection{Planning the Study}
Initially, existing SLRs were identified and evaluated, with the goal of mapping and identifying the gap in the existing literature. All identified SLRs \cite{santiago2012model} \cite{dias2007survey} \cite{loniewski2010systematic} \cite{nicolas2009generation} were, however, researching the usage of model-driven techniques in other fields, such as traceability management \cite{santiago2012model}, testing \cite{dias2007survey} and requirements engineering \cite{loniewski2010systematic} \cite{nicolas2009generation}. Based on these results, the need to evaluate previous research on model driven \textit{software} development was identified.

The next step was to define the research questions. The main research question was constructed to create a wide scope to be able to investigate which characteristics are most vital to consider when adopting MDSD. The sub-questions were constructed to provide more detailed answers for specific questions that are valuable to the industry and companies who are considering to implement MDSD.

@@

\SubSection{Conducting}
\textbf{Conducting the review}
\begin{itemize}
\item Identification of research (6.1)

@@

\SubSection{Reporting (probably skip)}
\textbf{Reporting the review}
\begin{itemize}
\item Specifying dissemination mechanisms (7.1)
\item Formatting the main report (7.2)
\item Evaluating the report (7.3)
\end{itemize}

@@

\Section{Acknowledgements}

\begin{itemize}
\item \textbf{these bulletins are from the assignment specification}
\item Describe and explain the research strategy (i.e. SLR) and investigation methods that will be used for the study. 
\item Motivate your choice of experiment using relevant references. 
\item Search string including keywords and used databases
\item inclusion/exclusion criteria
\item data extraction
\item data synthesis
\item quality assessment
\end{itemize}
